\begin{thebibliography}{99}
\vspace{0.5cm}
\noindent\textbf{Tiếng Anh}
\bibitem{agrawal1995} Agrawal, Rakesh, Srikant, Ramakrishnan (1995), ``Mining sequential patterns'', \textit{Proceedings of the 11th International Conference on Data Engineering (ICDE)}, 3-14, IEEE.
\bibitem{agrawal1994} Agrawal, Rakesh, Srikant, Ramakrishnan (1994), ``Fast algorithms for mining association rules'', \textit{Proceedings of the 20th International Conference on Very Large Data Bases (VLDB)}, 487-499.
\bibitem{bifet2007} Bifet, Albert, Gavald\`{a}, Ricard (2007), ``Learning from time-changing data with adaptive windowing'', \textit{Proceedings of the 7th SIAM International Conference on Data Mining (SDM)}, 443-448, SIAM.
\bibitem{msnbc2000} Cadez, Igor, Heckerman, David, Meek, Christopher, Smyth, Padhraic, White, Steven (2000), \textit{MSNBC.com Anonymous Web Data}, UCI Machine Learning Repository, \url{https://archive.ics.uci.edu/ml/datasets/MSNBC.com+Anonymous+Web+Data}.
\bibitem{fournier2017} Fournier-Viger, Philippe, Lin, Jerry Chun-Wei, Kiran, Rage Uday, Koh, Yun Sing, Thomas, Rincy (2017), ``A survey of sequential pattern mining'', \textit{Data Science and Pattern Recognition}, 1(1), 54-77.
\bibitem{gama2014} Gama, Jo{\~a}o, \v{Z}liobait{\.e}, Indr{\.e}, Bifet, Albert, Pechenizkiy, Mykola, Bouchachia, Abdelhamid (2014), ``A survey on concept drift adaptation'', \textit{ACM Computing Surveys}, 46(4), 1-37.
\bibitem{gueniche2013} Gueniche, Ted, Fournier-Viger, Philippe, Tseng, Vincent S. (2015), ``CPT+: Decreasing the time/space complexity of the Compact Prediction Tree'', \textit{Proceedings of the 19th Pacific-Asia Conference on Knowledge Discovery and Data Mining (PAKDD)}, 625-636, Springer.
\bibitem{hassani2019} Hassani, Marwan, Habich, Dirk, Lehner, Wolfgang (2019), ``BFSPMiner: An effective and efficient batch-free algorithm for mining sequential patterns over data streams'', \textit{Proceedings of the IEEE International Conference on Data Mining (ICDM)}, 230-239, IEEE.
\bibitem{ho2005} Ho, Shen-Shyang, Wechsler, Harry (2005), ``Mining frequent patterns from data streams with online, interactive constraints'', \textit{Proceedings of the 5th IEEE International Conference on Data Mining (ICDM)}, 653-656, IEEE.
\bibitem{kolter2011} Kolter, J. Zico, Johnson, Matthew J. (2011), ``REDD: A public data set for energy disaggregation research'', \textit{Proceedings of the SustKDD Workshop on Data Mining Applications in Sustainability}.
\bibitem{laxman2007} Laxman, Srivatsan, Tankala, Vikram, White, Ryen W. (2007), ``A fast algorithm for finding frequent episodes in event streams'', \textit{Proceedings of the 13th ACM SIGKDD International Conference on Knowledge Discovery and Data Mining}, 410-419, ACM.
\bibitem{mannila1997} Mannila, Heikki, Toivonen, Hannu, Verkamo, A. Inkeri (1997), ``Discovery of frequent episodes in event sequences'', \textit{Data Mining and Knowledge Discovery}, 1(3), 259-289.
\bibitem{marascu2006} Marascu, Alice, Masseglia, Florent (2006), ``Mining sequential patterns from data streams: a centroid approach'', \textit{Journal of Intelligent Information Systems}, 27(3), 291-307, Springer.
\bibitem{pei2001} Pei, Jian, Han, Jiawei, Mortazavi-Asl, Behzad, Pinto, Helen, Chen, Qiming, Dayal, Umeshwar, Hsu, Meichun (2001), ``PrefixSpan: Mining sequential patterns efficiently by prefix-projected pattern growth'', \textit{Proceedings of the 17th International Conference on Data Engineering (ICDE)}, 215-224, IEEE.
\bibitem{srikant1996} Srikant, Ramakrishnan, Agrawal, Rakesh (1996), ``Mining sequential patterns: Generalizations and performance improvements'', \textit{Proceedings of the 5th International Conference on Extending Database Technology (EDBT)}, 3-17, Springer.
\bibitem{wu2013} Wu, Xindong, Zhu, Xingquan, Wu, Gong-Qing, Ding, Wei (2013), ``Mining sequential patterns with gap constraints'', \textit{Journal of Computer Science and Technology}, 28(3), 472-483.
\bibitem{yan2003} Yan, Xifeng, Han, Jiawei, Afshar, Ramin (2003), ``CloSpan: Mining closed sequential patterns in large datasets'', \textit{Proceedings of the 3rd SIAM International Conference on Data Mining (SDM)}, 166-177, SIAM.
\bibitem{zaki2001} Zaki, Mohammed J. (2001), ``SPADE: An efficient algorithm for mining frequent sequences'', \textit{Machine Learning}, 42(1--2), 31-60.
\end{thebibliography}